---
title: "Baseline HPV Vaccination 2021 Project Report"
output: 
  html_document:
    df_print: paged
    code_foldering: hide
date: "`r format(Sys.time(), '%d %B, %Y')`"

params:
  HealthSystem: NA
  Q1_DBA: NA
  Q2: NA
  Q2_other: NA
  Q3: NA
  Q4a: NA
  Q4b: NA
  Q4c: NA
  Q5: NA
  Q5_Email: NA
  Q6: NA
  Q7: NA
  Q8: NA
  Q8_Email: NA
  Q9: NA
  Q10: NA
  Q10_other: NA
  Q11: NA
  Q11_other: NA
  Q12: NA
  Q12_other: NA
  Q13: NA
  Q13_amount: NA
  Q13_source: NA
  Q13_date: NA
  Q13_length: NA
  Q14: NA
  Q14_other: NA
  
  Q15: NA
  Q15_other: NA
  Q15_EHRversion: NA
  Q16: NA
  Q17: NA
  Q18: NA
  Q19: NA
  Q20: NA
  Q20_notes: NA 
  Q20_orders: NA
  Q20_other: NA
  Q21: NA
  Q21_text: NA
  Q22: NA
  Q22_notes: NA
  Q23: NA
  Q23_notes: NA 
  Q24: NA
  Q24_years: NA
  Q25: NA 
  Q26: NA
  Q26_other: NA
  
  Q1R: NA
  Q1R_other: NA
  Q2R: NA
  Q2R_other: NA
  Q3R: NA
  Q4R: NA
  FemAge1_total: NA
  FemAge1_dose1: NA
  FemAge1_dose2: NA      
  MenAge1_total: NA
  MenAge1_dose1: NA
  MenAge1_dose2: NA     
  BothAge1_total: NA     
  BothAge1_dose1: NA     
  BothAge1_dose2: NA     
  FemAge2_total: NA     
  FemAge2_dose1: NA      
  FemAge2_dose2: NA      
  FemAge2_mening: NA     
  FemAge2_tdap: NA      
  MenAge2_total: NA     
  MenAge2_dose1: NA      
  MenAge2_dose2: NA      
  MenAge2_mening: NA    
  MenAge2_tdap: NA       
  BothAge2_total: NA     
  BothAge2_dose1: NA     
  BothAge2_dose2: NA    
  BothAge2_mening: NA    
  BothAge2_tdap: NA
  FemAge3_total: NA
  FemAge3_dose1: NA
  FemAge3_dose2: NA
  FemAge3_mening: NA
  FemAge3_tdap: NA
  MenAge3_total: NA     
  MenAge3_dose1: NA
  MenAge3_dose2: NA
  MenAge3_mening: NA
  MenAge3_tdap: NA      
  BothAge3_total: NA
  BothAge3_dose1: NA
  BothAge3_dose2: NA
  BothAge3_mening: NA
  BothAge3_tdap: NA
  Q5R: NA
  Q5R_other: NA
  Q6R: NA  
  Q6R_details: NA
  Q6R_other: NA
  Q7R: NA
  Q7R_other: NA      
  Q8R: NA
  
  Q9R: NA
  Q9R_other: NA
  Q10aR: NA
  Q10bR: NA
  Q10cR: NA
  Q10dR: NA
  Q10eR: NA
  Q10fR: NA
  Q11R: NA
  Q12R: NA
  Q12R_other: NA
  Q13R: NA
  Q13R_other: NA
  Q14R: NA
  Q15R: NA
  Q16R: NA
  act1: NA
  act2: NA
  act3: NA
  act4: NA
  act5: NA
  act6: NA
  act7: NA
  act8: NA
  act9: NA
  act10: NA
  ppl1: NA
  ppl2: NA
  ppl3: NA
  ppl4: NA
  ppl5: NA
  ppl6: NA
  ppl7: NA
  ppl8: NA
  ppl9: NA
  ppl10: NA
  time1: NA
  time2: NA
  time3: NA
  time4: NA
  time5: NA
  time6: NA
  time7: NA
  time8: NA
  time9: NA
  time10: NA
  
  

---

<style type="text/css">

body{ /* Whole document */
      font-size: 16px;
      color: Gray;
      }
h1.title{
      font-size: 32px;
      color: Black;
      }
h1{
      font-size: 42px;
      color: Black;
      }
h2{ 
      font-size: 28px;
      color: DarkRed;
      }
h3{ 
      font-size: 28px;
      color: Red;
      }
h5{ 
      font-size: 16px;
      color: Gray;
      }      
h6{ 
      font-size: 16px;
      color: Black;
      font-weight: bold;
      }
pre{ /* Code block- determines spacing between lines */
      font-size: 14px;
      }   
code.r{
  font-size: 16px;
  color: Gray
  font-family: "Times New Roman", Times, serif;
  margin-bottom:3em;
}
p:first-of-type{
      font-style: italic;
      color: Gray;
      font-size: 16px;
}
.blackbox{
  padding: 1em 0em 0em 1em;
  color: white;
  border: 2px solid gray;
  border-radius: 10px;
}
.graybox{
  padding: 1em 1em 1em 1em;
  color: gray;
  border: 2px solid blue;
  border-radius: 10px;
}
.yellowhighlight{
  padding: 1em 1em 1em 1em;
  color: yellow;
  border: 5px solid yellow;
  border-radius: 10px;
}
</style>

```{css, echo=FALSE}
.answers {
  background-color: white;
  border: 3px solid black;
  font-weight: bold;
  color: light-gray;
  font-family: "Times New Roman", Times, serif;
}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(opts.label="kill_prefix")
```


\ 
\  

\  


<center><h1> **HPV SASI Dashboard** </h1></center>

\ 
\  
<h5>This is an html print-out of the baseline questionnaire on the Mission HPV dashboard. Please fill out all answers on the dashboard form and submit your responses there; this report is purely for your records and internal distribution. 
<br><br>
If you would like to print this as a pdf, right click on this screen to print. In the print options, select 'Save as pdf' and save the file to your preferred location. <br><br>
Jennifer & team- let me know what other information you'd like here :)  
</h5>

\  
\  

\n

### Demographics  
<h5>First, let's get some more information about your clinic and its demographics.</h5>  

\  

###### 1. System Name
::: {.blackbox data-latex=""}
`r params$HealthSystem`
:::

###### 1b. Doing Business as (DBA)
::: {.blackbox data-latex=""}
`r params$Q1_DBA`
:::

###### 2. Health System type?
::: {.blackbox data-latex=""}
`r params$Q2`
:::

###### 3.Total number of clinic sites in system
::: {.blackbox data-latex=""}
`r params$Q3`
:::
\  

:::: {.graybox data-latex=""}
###### 4a. City
::: {.blackbox data-latex=""}
`r params$Q4a` 
:::


###### 4b. State
::: {.blackbox data-latex=""}
`r params$Q4b`
:::


###### 4c. Zipcode
::: {.blackbox data-latex=""}
`r params$Q4c`
:::
::::
\  

###### 5. Name and title of Health System project lead
::: {.blackbox data-latex=""}
`r params$Q5`
:::

###### 6. Name and title of Health System QI lead
::: {.blackbox data-latex=""}
`r params$Q6`
:::


###### 7. Name and title of project clinical champion
::: {.blackbox data-latex=""}
`r params$Q7`
:::


###### 8. Name of an ACS lead
::: {.blackbox data-latex=""}
`r params$Q8`
:::


###### 8b. Email for ACS lead
::: {.blackbox data-latex=""}
`r params$Q8_Email`
:::


###### 9. Other ACS staff involved in the project
::: {.blackbox data-latex=""}
`r params$Q9`
:::
\  

:::: {.graybox data-latex=""}
###### 10. Are all clinic sites in the system participating in this project?
::: {.blackbox data-latex=""}
`r params$Q10`
:::


###### 10. Other specified (only applicable if answered 'No' above)
::: {.blackbox data-latex=""}
`r params$Q10_other`
:::
::::
\  

:::: {.graybox data-latex=""}
###### 11. Which service lines are participating in this HPV vaccination project?
::: {.blackbox data-latex=""}
`r params$Q11`
:::


###### 11a. Other specified
::: {.blackbox data-latex=""}
`r params$Q11_other`
:::
::::
\  

:::: {.graybox data-latex=""}
###### 12. Are any of the following types of clinics participating in this HPV vaccination project?
::: {.blackbox data-latex=""}
`r params$Q12`
:::

###### 12. Other specified (if chose 'Other' above)
::: {.blackbox data-latex=""}
`r params$Q12_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 13. Does this project have any project-specific funding?
::: {.blackbox data-latex=""}
`r params$Q13`
:::


###### 13. Amount (only applicable if said 'yes' to project-specific funding source)
::: {.blackbox data-latex=""}
`r params$Q13_amount`
:::


###### 13. Source (only applicable if said 'yes' to project-specific funding source)
::: {.blackbox data-latex=""}
`r params$Q13_source`
:::


###### 13. Date (only applicable if said 'yes' to project-specific funding source)
::: {.blackbox data-latex=""}
`r params$Q13_date`
:::


###### 13. Length (only applicable if said 'yes' to project-specific funding source)
::: {.blackbox data-latex=""}
`r params$Q13_length`
:::
::::

\ 

:::: {.graybox data-latex=""}
###### 14. Is this project part of...?
::: {.blackbox data-latex=""}
`r params$Q14`
:::


###### 14. Other specified (if selected 'Other' above)
::: {.blackbox data-latex=""}
`r params$Q14_other`
:::
::::

\  
\  

\n

### System Background

<h5>Now, you'll provide information on the data systems your health system uses. Please complete this information to the best of your knowledge.</h5>

\  

:::: {.graybox data-latex=""}
###### 15. EHR System
::: {.blackbox data-latex=""}
`r params$Q15`
:::

###### 15. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q15_other`
:::
::::

\  

###### 16. Populatoin management system and version
::: {.blackbox data-latex=""}
`r params$Q16`
:::

###### 17. Our system is currently set up to:
::: {.blackbox data-latex=""}
`r params$Q17`
:::

###### 18. At this moment, our EHR system has:
::: {.blackbox data-latex=""}
`r params$Q18`
:::

###### 19. At this moment, our State Immunization Registry:
::: {.blackbox data-latex=""}
`r params$Q19`
:::

###### 20. Does your system have standing orders for HPV vaccination?
::: {.blackbox data-latex=""}
`r params$Q20`
:::

###### 21. Are patients scheduled for the next HPV vaccination visit before they leave the office?
::: {.blackbox data-latex=""}
`r params$Q21`
:::

###### 22. If the HPV vaccine is declined, is it system policy to recommend it again at future visits?
::: {.blackbox data-latex=""}
`r params$Q22`
:::

###### 23. Has your system used quality improvement to increase HPV vaccination rates in the past?
::: {.blackbox data-latex=""}
`r params$Q23`
:::

###### 24. Has your system completed a HPV VACs Systems and Strategies Inventory with ACS in the past?
::: {.blackbox data-latex=""}
`r params$Q24`
:::

###### 25. Which of the following training and education activities has your system already conducted to increase HPV vaccination rates? *(with or without support from ACS)*
::: {.blackbox data-latex=""}
`r params$Q25`
:::

\  

:::: {.graybox data-latex=""}
###### 26. Which of the following interventions to increase HPV vaccination has your system already implemented? *(with or without support from ACS)*
::: {.blackbox data-latex=""}
`r params$Q26`
:::

###### 26. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q26_other`
:::
::::


\  
\  

\n

### Vaccination Rates

<h5>Calculate **baseline** vaccination rates as the number of active medical patients ages 9-13 who were up-to-date with HPV, TDap, and Meningococcal vaccines in 2020. Separate vaccine rates by vaccine, age and sex (if possible). **If unable to separate by sex**, enter the vaccination rates data **for males and females combined.**</h5>

\ 

:::: {.graybox data-latex=""}
###### 1. How are you defining your active patient populations?
::: {.blackbox data-latex=""}
`r params$Q1R`
:::

###### 1. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q1R_other`
:::
::::

\  

###### 2. For what ages are you reporting?
::: {.blackbox data-latex=""}
`r params$Q2R`
:::

###### 3. Can you pull rate data by sex?
::: {.blackbox data-latex=""}
`r params$Q3R`
:::

\  

###### Ages 9-10
```{r, echo=FALSE, results="asis"}
rates1 <- data.frame(rbind(c(params$FemAge1_total, params$FemAge1_dose1, params$FemAge1_dose2),
                           c(params$MenAge1_total, params$MenAge1_dose1, params$MenAge1_dose2),
                           c(params$BothAge1_total, params$BothAge1_dose1, params$BothAge1_dose2)))

rownames(rates1)<- c("Females", "Males", "Combined")
colnames(rates1)<- c("Total", "1+ dose", "2 doses")
knitr::kable(rates1)
```

###### Ages 11-12
```{r, echo=FALSE, results="asis"}
rates2 <- data.frame(rbind(c(params$FemAge2_total, params$FemAge2_dose1, params$FemAge2_dose2, params$FemAge2_mening, params$FemAge2_tdap),
                           c(params$MenAge2_total, params$MenAge2_dose1, params$MenAge2_dose2, params$MenAge2_mening, params$MenAge2_tdap),
                           c(params$BothAge2_total, params$BothAge2_dose1, params$BothAge2_dose2, params$BothAge2_mening, params$BothAge2_tdap)))

rownames(rates2)<- c("Females", "Males", "Combined")
colnames(rates2)<- c("Total", "1+ dose", "2 doses", "Meningococcus", "Tdap")
knitr::kable(rates2)
```

###### Ages 13
```{r, echo=FALSE, results="asis"}
rates3 <- data.frame(rbind(c(params$FemAge3_total, params$FemAge3_dose1, params$FemAge3_dose2, params$FemAge3_mening, params$FemAge3_tdap),
                           c(params$MenAge3_total, params$MenAge3_dose1, params$MenAge3_dose2, params$MenAge3_mening, params$MenAge3_tdap),
                           c(params$BothAge3_total, params$BothAge3_dose1, params$BothAge3_dose2, params$BothAge3_mening, params$BothAge3_tdap)))

rownames(rates3)<- c("Females", "Males", "Combined")
colnames(rates3)<- c("Total", "1+ dose", "2 doses", "Meningococcus", "Tdap")
knitr::kable(rates3)
```

\  



###### 4. Please share anything else about your baseline data you'd like us to know:
::: {.blackbox data-latex=""}
`r params$Q4R`
:::

\  

:::: {.graybox data-latex=""}
###### 5. What was the primary data source used to calculate your vaccination rates?
::: {.blackbox data-latex=""}
`r params$Q5R`
:::

###### 5. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q5R_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 6. Did you use a secondary data source?
::: {.blackbox data-latex=""}
`r params$Q6R`
:::

###### 6. What secondary sources were used (select all that apply)? (if applicable)
::: {.blackbox data-latex=""}
`r params$Q6R_details`
:::

###### 6. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q6R_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 7. Were you unable to report any of the requested data?
::: {.blackbox data-latex=""}
`r params$Q7R`
:::

###### 7. Describe what you were unable to report and why
::: {.blackbox data-latex=""}
`r params$Q7R_other`
:::
::::

\  

###### 8. Are you working on your reporting capacity and anticipate submitting updated data in the next few months?
::: {.blackbox data-latex=""}
`r params$Q8R`
:::

\  
\  

\n

### Project Activity Plan

<h5>This last section will prompt you about your project activity plan.</h5>

\ 

:::: {.graybox data-latex=""}
###### 9. What other data do we need to obtain before establishing our goal?
::: {.blackbox data-latex=""}
`r params$Q9R`
:::

###### 9. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q9R_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 10a. What is our specific numerical goal?
::: {.blackbox data-latex=""}
`r params$Q10aR`
:::

###### 10b. What is our target population?
::: {.blackbox data-latex=""}
`r params$Q10bR`
:::

###### 10c. Where will we do it?
::: {.blackbox data-latex=""}
`r params$Q10cR`
:::


###### 10d. What is the time period to achieve this aim?
::: {.blackbox data-latex=""}
`r params$Q10dR`
:::

###### 10e. Why is it important to do this now?
::: {.blackbox data-latex=""}
`r params$Q10eR`
:::
::::

\  

:::: {.yellowhighlight data-latex=""}
###### 10f. Now, combine the above into a single **Aim** statement
::: {.blackbox data-latex=""}
**We aim to...**
`r params$Q10fR`
:::
::::

\  

###### 11. Which of the following HPV vaccination training and education actitivities will we conduct?
::: {.blackbox data-latex=""}
`r params$Q11R`
:::

\  

:::: {.graybox data-latex=""}
###### 12. Which of the following interventions to increase HPV vaccination will we implement?
::: {.blackbox data-latex=""}
`r params$Q12R`
:::

###### 12. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q12R_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 13. What forms of support would the health system like from the ACS staff partner?
::: {.blackbox data-latex=""}
`r params$Q13R`
:::

###### 13. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q13R_other`
:::
::::

\  

###### 14. How will we communicate with providers, staff, and leadership about project kickoff, goal and updates?
::: {.blackbox data-latex=""}
`r params$Q14R`
:::

###### 15. How will we build and maintain excitement and momentum for the project?
::: {.blackbox data-latex=""}
`r params$Q15R`
:::

###### 16. How will we celebrate and share success?
::: {.blackbox data-latex=""}
`r params$Q16R`
:::

###### 17. What specific actions will we take to implement the above interventions and trainings to meet our goal?
```{r, echo=FALSE, results="asis"}
table<- data.frame(rbind(c(params$act1, params$time1, params$ppl1),
                           c(params$act2, params$time2, params$ppl2),
                           c(params$act3, params$time3, params$ppl3),
                           c(params$act4, params$time4, params$ppl4),
                           c(params$act5, params$time5, params$ppl5),
                           c(params$act6, params$time6, params$ppl6),
                           c(params$act7, params$time7, params$ppl7),
                           c(params$act8, params$time8, params$ppl8),
                           c(params$act9, params$time9, params$ppl9),
                           c(params$act10, params$time10, params$ppl10)))

table <- table[!apply(is.na(table) | table =="", 1, all), ]

names(table)<- c("Activity", "Timeline", "Person/People Responsible")
knitr::kable(table)
```

\  




\  
\  

