---
title: "Final Report"
output: 
  html_document:
    df_print: paged
    code_foldering: hide
date: "`r format(Sys.time(), '%d %B, %Y')`"

params:
  HealthSystem: NA
  Q1FU: NA
  Q1FU_other: NA
  Q2FU: NA 
  Q2FU_other: NA 
  Q3FU: NA
  Q4FU: NA
   
  FemFUAge1_total: NA
  FemFUAge1_dose1: NA 
  FemFUAge1_dose2: NA
  MenFUAge1_total: NA
  MenFUAge1_dose1: NA 
  MenFUAge1_dose2: NA
  BothFUAge1_total: NA
  BothFUAge1_dose1: NA
  BothFUAge1_dose2: NA
      
  FemFUAge2_total: NA
  FemFUAge2_dose1: NA
  FemFUAge2_dose2: NA
  FemFUAge2_mening: NA
  FemFUAge2_tdap: NA
  MenFUAge2_total: NA
  MenFUAge2_dose1: NA
  MenFUAge2_dose2: NA
  MenFUAge2_mening: NA
  MenFUAge2_tdap: NA
  BothFUAge2_total: NA
  BothFUAge2_dose1: NA
  BothFUAge2_dose2: NA
  BothFUAge2_mening: NA
  BothFUAge2_tdap: NA
      
  FemFUAge3_total: NA
  FemFUAge3_dose1: NA
  FemFUAge3_dose2: NA
  FemFUAge3_mening: NA
  FemFUAge3_tdap: NA
  MenFUAge3_total: NA
  MenFUAge3_dose1: NA
  MenFUAge3_dose2: NA
  MenFUAge3_mening: NA
  MenFUAge3_tdap: NA
  BothFUAge3_total: NA
  BothFUAge3_dose1: NA
  BothFUAge3_dose2: NA
  BothFUAge3_mening: NA
  BothFUAge3_tdap: NA
  
  Q5FU: NA
  Q5FU_text: NA
  Q6FU: NA
  Q7FU: NA
  Q7FU_other: NA
  Q8FU: NA 
  Q8FU_other: NA
  Q9FU: NA
  Q9FU_other: NA
  Q10FU: NA
  Q11FU: NA
  Q12FU: NA 
  Q13FU: NA
  Q13FU_other: NA
  Q14FU: NA
  Q14FU_other: NA
  Q15FU: NA
  Q16FU: NA
  Q17FU: NA
  Q18FU: NA
  Q18FU_more: NA
  
  

---

<style type="text/css">

body{ /* Whole document */
      font-size: 16px;
      color: Gray;
      }
h1.title{
      font-size: 32px;
      color: Black;
      }
h1{
      font-size: 42px;
      color: Black;
      }
h2{ 
      font-size: 28px;
      color: DarkRed;
      }
h3{ 
      font-size: 28px;
      color: Red;
      }
h5{ 
      font-size: 16px;
      color: Gray;
      }      
h6{ 
      font-size: 16px;
      color: Black;
      font-weight: bold;
      }
pre{ /* Code block- determines spacing between lines */
      font-size: 14px;
      }   
code.r{
  font-size: 16px;
  color: Gray
  font-family: "Times New Roman", Times, serif;
  margin-bottom:3em;
}
p:first-of-type{
      font-style: italic;
      color: Gray;
      font-size: 16px;
}
.blackbox{
  padding: 1em 0em 0em 1em;
  color: white;
  border: 2px solid gray;
  border-radius: 10px;
}
.graybox{
  padding: 1em 1em 1em 1em;
  color: gray;
  border: 2px solid blue;
  border-radius: 10px;
}
.yellowhighlight{
  padding: 1em 1em 1em 1em;
  color: yellow;
  border: 5px solid yellow;
  border-radius: 10px;
}
</style>

```{css, echo=FALSE}
.answers {
  background-color: white;
  border: 3px solid black;
  font-weight: bold;
  color: light-gray;
  font-family: "Times New Roman", Times, serif;
}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(opts.label="kill_prefix")
```


\ 
\  

\  


<center><h1> **`r toupper(params$HealthSystem)`** </h1></center>

\ 
\  
<h5>This is an html print-out of the final questionnaire on the Mission HPV dashboard. Please fill out all answers on the dashboard form and submit your responses there; this report is purely for your records and internal distribution. 
<br><br>
If you would like to print this as a pdf, right click on this screen to print. In the print options, select 'Save as pdf' and save the file to your preferred location. <br><br>
Jennifer & team- let me know what other information you'd like here :)  
</h5>

\  
\  

### Updated Rates 
<h5>Below were your provided responses for the demographics section of the Baseline Questionnaire. If you do not see anything listed, you have not yet provided that response.</h5>  

\  

:::: {.graybox data-latex=""}
###### 1. How are you defining your active patient populations?
::: {.blackbox data-latex=""}
`r params$Q1FU`
:::

###### 1. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q1FU_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 2. For what ages are you reporting?
::: {.blackbox data-latex=""}
`r params$Q2FU`
:::

###### 2. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q2FU_other`
:::
::::

\  

###### 3. Can you pull rate data by sex?
::: {.blackbox data-latex=""}
`r params$Q3FU`
:::

\  

###### Ages 9-10
```{r, echo=FALSE, results="asis"}
rates1 <- data.frame(rbind(c(params$FemFUAge1_total, params$FemFUAge1_dose1, params$FemFUAge1_dose2),
                           c(params$MenFUAge1_total, params$MenFUAge1_dose1, params$MenFUAge1_dose2),
                           c(params$BothFUAge1_total, params$BothFUAge1_dose1, params$BothFUAge1_dose2)))

rownames(rates1)<- c("Females", "Males", "Combined")
colnames(rates1)<- c("Total", "1+ dose", "2 doses")
knitr::kable(rates1)
```

###### FUAges 11-12
```{r, echo=FALSE, results="asis"}
rates2 <- data.frame(rbind(c(params$FemFUAge2_total, params$FemFUAge2_dose1, params$FemFUAge2_dose2, params$FemFUAge2_mening, params$FemFUAge2_tdap),
                           c(params$MenFUAge2_total, params$MenFUAge2_dose1, params$MenFUAge2_dose2, params$MenFUAge2_mening, params$MenFUAge2_tdap),
                           c(params$BothFUAge2_total, params$BothFUAge2_dose1, params$BothFUAge2_dose2, params$BothFUAge2_mening, params$BothFUAge2_tdap)))

rownames(rates2)<- c("Females", "Males", "Combined")
colnames(rates2)<- c("Total", "1+ dose", "2 doses", "Meningococcus", "Tdap")
knitr::kable(rates2)
```

###### FUAges 13
```{r, echo=FALSE, results="asis"}
rates3 <- data.frame(rbind(c(params$FemFUAge3_total, params$FemFUAge3_dose1, params$FemFUAge3_dose2, params$FemFUAge3_mening, params$FemFUAge3_tdap),
                           c(params$MenFUAge3_total, params$MenFUAge3_dose1, params$MenFUAge3_dose2, params$MenFUAge3_mening, params$MenFUAge3_tdap),
                           c(params$BothFUAge3_total, params$BothFUAge3_dose1, params$BothFUAge3_dose2, params$BothFUAge3_mening, params$BothFUAge3_tdap)))

rownames(rates3)<- c("Females", "Males", "Combined")
colnames(rates3)<- c("Total", "1+ dose", "2 doses", "Meningococcus", "Tdap")
knitr::kable(rates3)
```

\  

###### 4. Please share anything else about your baseline data you'd like us to know:
::: {.blackbox data-latex=""}
`r params$Q4FU`
:::

\  
\  

### Additional Info

\  

:::: {.graybox data-latex=""}
###### 5. Did you use the same primary data source for all pulls?
::: {.blackbox data-latex=""}
`r params$Q5FU`
:::

###### 5. Additional text
::: {.blackbox data-latex=""}
`r params$Q5FU_text`
:::
::::

\  

###### 6. Did we meet our project goals?
::: {.blackbox data-latex=""}
`r params$Q6FU`
:::

\  

:::: {.graybox data-latex=""}
###### 7. We conducted or participated in the following HPV vaccination training and education activities in 2020: *(check all that apply)*
::: {.blackbox data-latex=""}
`r params$Q7FU`
:::

###### 7. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q7FU_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 8. Did you participate in any of the following in 2020?
::: {.blackbox data-latex=""}
`r params$Q8FU`
:::

###### 8. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q8FU_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 9. We implemented the following interventions to increase HPV vaccination in 2020:
::: {.blackbox data-latex=""}
`r params$Q9FU`
:::

###### 9. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q9FU_other`
:::
::::

\  

###### 10. How many providers did we train?
::: {.blackbox data-latex=""}
`r params$Q10FU`
:::

###### 11. What was the average number of training hours per provider?
::: {.blackbox data-latex=""}
`r params$Q11FU`
:::

###### 12. How many other staff did we educate?
::: {.blackbox data-latex=""}
`r params$Q12FU`
:::

\  

:::: {.graybox data-latex=""}
###### 13. We used the following tools and resources:
::: {.blackbox data-latex=""}
`r params$Q13FU`
:::

###### 13. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q13FU_other`
:::
::::

\  

:::: {.graybox data-latex=""}
###### 14. What roles did ACS play in this project?
::: {.blackbox data-latex=""}
`r params$Q14FU`
:::

###### 14. Other specified (if applicable)
::: {.blackbox data-latex=""}
`r params$Q14FU_other`
:::
::::

\  

###### 15. What were the successes and challenges of this project?
::: {.blackbox data-latex=""}
`r params$Q15FU`
:::

###### 16. What is our plan to sustain the changes we made in this project?
::: {.blackbox data-latex=""}
`r params$Q16FU`
:::

###### 17. Is there anything else to add about this project?
::: {.blackbox data-latex=""}
`r params$Q17FU`
:::

\  

:::: {.graybox data-latex=""}
###### 18. Will our system continue to work with ACS to increase our HPV vaccination rates?
::: {.blackbox data-latex=""}
`r params$Q18FU`
:::

###### 18. Additional text (if applicable)
::: {.blackbox data-latex=""}
`r params$Q18FU_more`
:::
::::

\  
\  

